\documentclass[12pt]{article}

\title{\bf\Large  On Soft Loss of Stability in  Ocean Circulation Box Model with Turbulent Fluxes}
\author{\underline{Davydov A.A.}$^{1, 2}$, Zosimov S.O.$^{1}$}
\date{}

\begin{document}

\begin{center}
	\maketitle
	{\large\textit{1. {Lomonosov Moscow State University}} \\
		\large\textit{2. {National University of Science and Technology MISIS}}}
\end{center}

We consider a two dimensional system of ordinary differential equations that provides a qualitative description of the thermohaline circulation locally  in the upper layer of water in ocean \cite{DM07}, \cite{DM07a}, \cite{We82}. We show that in a generic finite parametric case of transfer functions from the system  the soft loss of stability of a steady state in this system is described by the appearance of nonzero  fixed points of composition of pair of two involutions of the real line with fixed point at zero, which are defined by the system. The respective bifurcation diagrams in the space of parameters are also described.

The study was financially supported by the Russian Science Foundation, project no.~19-11-00223

\begin{thebibliography}{99}
    
\bibitem{DM07}  Davydov A.A.,  Melnikov N.B., Soft Loss of Stability in an Ocean Circulation Box Model with Turbulent Fluxes, Proc. Steklov Inst. Math., 259 (2007), 6-15

\bibitem{DM07a}  Davydov A.A.,  Melnikov N.B., Andronov-Hopf bifurcation in simple double diffusion models, Russian Math. Surveys, 62:2 (2007), 382-384

\bibitem{We82}  Welander  P.A., A simple heat-salt oscillator // Dyn. Atmos. and Oceans. 1982. V. 6, N 4. P. 233-242.

\end{thebibliography}

%Обязательна информация об авторе
\end{document}

