\documentclass[12pt]{article}

\title{\bf\Large Graphs of Dynamical Systems on Surfaces and Efficient Algorithms for Their Distinguishing}
\author{Malyshev D.S.}
\date{}


\begin{document}

\begin{center}
	\maketitle
	{\large\textit{National Research University Higher School of Economics}}
\end{center}

I was privileged, and I am honoured to be a coauthor of \mbox{Prof. O.V. Pochinka} in the papers \cite{GMPZ16}--\cite{MMP21}.
They are devoted to combinatorial (predominantly, graph) invariants of some dynamical systems classes and efficient (mostly, polynomial-time) 
algorithms for solving the isomorphism problem for them. My talk will be devoted to these results, which will be dedicated to 50th-anniversary
of O.V. 


\begin{thebibliography}{99}
\bibitem{GMPZ16} Grines V.Z., Malyshev D.S., Pochinka O.V., Zinina S.Kh. Efficient algorithms for the recognition of topologically conjugate gradient-like diffeomorhisms // Regular and Chaotic Dynamics. 2016. Vol. 21. No. 2. P. 189--203.
\bibitem{KMP18} Kruglov V.E., Malyshev D.S., Pochinka O.V. Topological classification of $\Omega$-stable flows on surfaces by means of effectively distinguishable multigraphs // Discrete and Continuous Dynamical Systems. 2018. Vol. 38. No. 9. P. 4305--4327.
\bibitem{KMP18} Kruglov V.E., Malyshev D.S., Pochinka O.V. On algorithms that effectively distinguish gradient-like dynamics on surfaces // Arnold Mathematical Journal. 2018. Vol. 4. No. 3--4. P. 483--504.
\bibitem{GGPM20} Grines V.Z., Gurevich E.Y., Pochinka O.V., Malyshev D.S. On topological classification of Morse-Smale diffeomorphisms on the sphere $S^n(n>3)$ // Nonlinearity. 2020. Vol. 33. No. 12. P. 7088--7113.
\bibitem{KMPS20} Kruglov V.E., Malyshev D.S., Pochinka O.V., Shubin D. On topological classification of gradient-like Flows on an $n$-sphere in the sense of topological conjugacy // Regular and Chaotic Dynamics. 2020. Vol. 25. No. 6. P. 716--728.
\bibitem{MMP21} Malyshev D.S., Morozov A.I., Pochinka O.V. Combinatorial invariant for Morse-Smale diffeomorphisms on surfaces with orientable heteroclinic // Chaos. 2021. Vol. 31. No. 2. Article 023119.
\end{thebibliography}

\end{document}
