


\maketitle
\begin{center}
	{\large\textit{Center of Integrable Systems, Yaroslavl State University}}
\end{center}


Mackey--Glass equation was first considered in \cite{MaGla1977} and was used to describe the concentration of blood cells. It is a differential equation with delay
$$
\frac{d u}{dt}=
- \beta u+\frac{\alpha u(t - h) }{1 + (u(t - h))^{\gamma}}. \eqno{(1)}
$$
Here parameters $\alpha,\beta,\gamma,h$ and unknown function $u(t)$ are positive.

We consider a generalization of the Mackey--Glass equation:
$$
\frac{d u}{dt}=- \beta u + \frac{\alpha\big(u(t - h_1) + \ldots+u(t- h_n)\big)}{1 + \big(\big(u(t - h_1) + \ldots+u(t- h_n)\big)\big)^{\gamma}}.\eqno{(2)} 
$$
Here $n$ is natural, $0<h_1<\ldots<h_n$.
The difference from the traditional Mackey--Glass equation (1) is the number of delays.

For a generalized equation, we consider the case of the large parameter $\gamma$. As $\gamma$ tends to infinity, the function $\frac{1}{1+w^\gamma}$ on the right side of the differential equation tends to the threshold function
$$
F(w)\stackrel{\rm def}{=}
\lim\limits_{\gamma\rightarrow+\infty} \frac{1}{1+w^\gamma}=
\left\lbrace\begin{array}{cl}
	1, & 0<w<1,\\
	\frac{1}{2}, & w=1,\\
	0, & w>1.
\end{array}\right.
$$
As a limit object for (2), we obtain the equation
$$\dot{u}=-\beta u+\alpha w F(w),\eqno{(3)}$$
where $w(t)=u(t-h_1)+\ldots+u(t-h_n)$.

We study the question of the existence and stability of a periodic solution of the equation (3).

This work was supported by the Russian Science Foundation (project No. 21-71-30011)

\begin{thebibliography}{99}
	\bibitem{MaGla1977} Mackey M. C. and Glass L. Oscillation and chaos in physiological
	control systems. Science. 1977. V. 197, No. 4300.  P. 287--289.
\end{thebibliography}

